### 2021-03-25 Chapter-2/Chapter-2.tex
Updates from Overleaf

Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same to the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the kernel of the operating system. We list two examples here. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).

@@

While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction.

>>>>

Some other side-channel targets also include spell checking tools, and font libraries~\cite{xu2015controlled}. The attack to font libraries is essentially the same as the attack to the graphic library like GTK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target on the kernel of the operating system. We list two examples here. One example is the to use the side-channel attacks to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time.

@@

While there are several existing work on side-channel leakage detections, we find it very hard to apply existing methods to identify controlled-channel attacks. According to Table~\ref{table:related_work}, existing methods can be classified into two categories, tools based on the trace comparison and tools based on the abstraction. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR.
